---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r,echo=TRUE}
data<-read.csv("activity/activity.csv",colClasses="character")
library(dplyr)
data[,2]<-as.Date(data[,2],"%Y-%m-%d")
data[,3]<-as.numeric(data[,3])
data[,1]<-as.numeric(data[,1])
data2<-subset(data,!is.na(data[,1]))
```

## What is mean total number of steps taken per day?
```{r,echo=TRUE}
s<-summarise(group_by(data2,date),total=sum(steps))
hist(s$total)
summarise(group_by(data2,date),mean=mean(steps))
summarise(group_by(data2,date),median=median(steps))
```


## What is the average daily activity pattern?
```{r,echo=TRUE}
v<-summarise(group_by(data2,interval),meanInterval=mean(steps))
plot(v$interval,v$meanInterval,type="l",xlab="Interval",ylab="average steps for interval")
filter(v,meanInterval==max(v$meanInterval))
```


## Inputing missing values
```{r,echo=TRUE}
missing<-subset(data,is.na(data[,1]))
nrow(missing)
i<-1
for(k in 1:8)
{
for(j in 1:288)
{
missing$steps[i]<-v$meanInterval[j]
i<-i+1
}
}
Final<-rbind(data2,missing)
Final<-arrange(Final,date)
s<-summarise(group_by(Final,date),total=sum(steps))
hist(s$total)
summarise(group_by(Final,date),mean=mean(steps))
summarise(group_by(Final,date),median=median(steps))
```
The values estimated above are definitely different from the first part of the assignment. Adding the missing values have increased the y axis level to 35 whereas in the first part of the assignment the y axis level was 25.
 
## Are there differences in activity patterns between weekdays and weekends?
```{r,echo=TRUE}
F<-mutate(Final,day=factor("weekday",levels=c("weekday","weekend")))
for(i in 1:17568)
{
if(weekdays(F[i,2])=="Sunday" || weekdays(F[i,2])=="Saturday"){F[i,4]<-"weekend"} else{F[i,4]<-"weekday"}
}
v<-summarise(group_by(F,day,interval),meanInterval=mean(steps))
library(lattice)
xyplot(meanInterval~interval|day,data=v,type="l",col="blue",layout=c(1,2))
```